---
title: "Peer Review for Min Jung"
output: html_document
date: "2026-03-22"
---
Your code is not runable in your markdown file. You to insert chunks so then you can run the actual code. It should look like what I have done below. Then you can run all chunks. Then anything that doesn't need to be run can be in the white space in between. I have shown an example below for the first two parts of your code. To insert teh chunks you can use the code tab at the very top and insert chunks. 

```{r}
library(dplyr)
library(tidyr)
library(readr)
```

#====================================
###dplyr provides functions such as:

  #filter() → choose rows based on conditions

  #select() → choose columns

  #arrange() → sort rows

  #mutate() → create new variables

  #summarize() → calculate summary statistics

# 2. Load data
```{r}
genotypes <- read_tsv("https://raw.githubusercontent.com/EEOB-BioData/BCB5460_Spring2026/main/assignments/UNIX_Assignment/fang_et_al_genotypes.txt")

snp_pos <- read_tsv("https://raw.githubusercontent.com/EEOB-BioData/BCB5460_Spring2026/main/assignments/UNIX_Assignment/snp_position.txt")
```

Because I could not run all the chunks it's hard to know if the entire code works or not. I will note anything that looks like it would not work 

# 5. Prepare SNP position table
I think you need to reference your data that you are trying to use the select command on. In this case I think it would snp_positions. So you would do snp_positions %>% then the rest of your code 

# 6. Join genotype and position data
In this code snp_info doesn't exist so you would need to create it in the line above. Also be careful joining how you have it written because geno_df doesn't have a column title of "SNP_ID" (I think it's sample_ID) so I don't think it would join the data correctly. 

# 7. Separate maize and teosinte groups
Make sure your naming conventions are consitent. In step 6 your data is "combined" but in step 7 your data is "combined_data"

I think you need to join back the combined_data and the maize/teosinte_data because I don't think you can add two different data column that that together. 

# 9. Function to create chromosome files
It is really hard to tell if this is going to run without errors without actually running the code. It looks like it should work but I don't know for certain. 

# Data visulaization 
You are missing 2/3 data visualization elements. 

