---
title: "Petersen_R_Assignment_review_by_Valerie"
author: "Valerie Yu"
date: "`r Sys.Date()`"
output: 
  pdf_document: 
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readr)
library(tidyverse)
```

# Review overall comments
* Your markdown is very cleanly written and easy to understand!
* All code ran without major error. I did get `Warning: NAs introduced by coercion` once, but the code still ran and produced the graph.

## PART 1 Review

### Data Inspection
* Very thorough on data inspection with each command purpose explained and answer commented.
* I liked how you described the variables important for the assignment.
* No issues, all ran smoothly.

### Data Processing
* Your final files appear to be sorted alphanumerically by position and are not in increasing or decreasing order.
* Specifically, looking at `CSV_files /maize_chr_10_decrease.csv`, the positions on: 
    - Line 17   (61,763,079)
    - Line 18   (6,121,326)  
    - Line 19   (43,936,126) 
* Line 17 is greater than Line 18, but Line 18 is less than Line 19.

* I think the error might have been when you transposed the data. You comment that the data is now character and convert to data frame, but that still left `Position` as a character.
* After your *merge* and before your *function*, I entered:
```{r, eval=FALSE}
typeof(Maize_merge_2$Position) # this produced Character
typeof(Teosinte_merge_2$Position) # this produced Character
```
* I think this caused your function to sort incorrectly since `Position` remains a character.
* After your *merge* and before your *function*, I added:
```{r, eval=FALSE}
Maize_merge_2$Position <- as.numeric(Maize_merge_2$Position)
Teosinte_merge_2$Position <- as.numeric(Teosinte_merge_2$Position)
typeof(Maize_merge_2$Position) # this produced Double
typeof(Teosinte_merge_2$Position) # this produced Double
```
* Then when I re-ran the rest of your code, the final files no longer sorted alphanumerically.

* You have `cdv_marker_id` at the end of your files and your first coloumn is titled `SAMPLE_ID`. I'd change this to fit the instructions, which say: __All our files will be formatted such that the first column is "SNP_ID", the second column is "Chromosome", the third column is "Position", and subsequent columns are genotype data from either  maize or teosinte individuals.__

* Outside of that, everything else looked good and made sense. 
* When I ran everything, it generated the csv files in the main folder and not the `CSV_files` folder. Not a huge deal but you could write it directly into `CSV_files` so when it's run it won't duplicate in `R_Assignment_BCB5460` 
* I should have deleted all edits/test-code I added and any duplicate test-csv files generated.  I only pushed my review .Rmd and .pdf so hopefully none of your original markdown code should be altered.

## PART 2 Review

### SNPs per chromosome
* I did it slightly different, but I think the distribution across chromosomes resulted in the same pattern!
* I like your ten plots using facet wrap. The x-axis is a bit hard to read, but that could just be my window size.

### Missing data and amount of heterozygosity and homozygosity
* No issues, all ran smoothly with graph showing up.

### Your own visualization
* No issues, all ran smoothly with graph showing up.


*End of my review.*

Valerie Yu